{\fontsize{100}{120}\selectfont Real-Time Activity Classification by Matched Filtering Using Body-Worn Accelerometers}

### 2016-11-07 notes/poster/poster.tex
Incrementals to poster.

%%%%%%%%%%%%%%%%%%%%%
% Activity Training %
%%%%%%%%%%%%%%%%%%%%%
\section{Activity Training}
We are able to identify an individual's activity by matching the signal to a reference template.
We develop a reference template for our matched-filter directly from a subset of the person's motion signature.
The individual performs a specified activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
For a given activity, we attempt to find the representative signal $\textbf{s}$ of our individual's activity to be our template for our matched-filter.

@@

To assess the real-time processing potential of the algorithms outlined in this paper, a throughput assessment was performed on the MSP432P401R microcontroller with varying parameters.
The Texas Instruments - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor.
Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, an IEEE 754-compliant single-precision Floating-Point Unit (FPU), and Memory Protection Unit (MPU).
The single-precision processing capability on this unit provides us with the dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
The 64 kB of SRAM provides sufficient space to process the results found in figure \ref{fig:timing} and
the 256 kB is more than enough flash memory to store the program and data references.
The clock frequency operates at 48 MHz which drives the execution speed.

>>>>

%%%%%%%%%%%%%%%%%%%%%
% Activity Training %
%%%%%%%%%%%%%%%%%%%%%
\section{Activity Training}
We are able to identify an individual's activity by matching the signal to a reference template.
We develop our reference for our matched-filter directly from a subset of the person's motion signature.
The individual performs a specified activity over a specified amount of time and we select the sub-interval of time that we find best represents the user's motion signature.
For a given activity, we attempt to find the representative signal $\textbf{s}$ of our individual's activity to be our template for our matched-filter.

@@

To assess the real-time processing potential of the algorithms outlined in this paper, a throughput assessment was performed on the MSP432P401R microcontroller with varying parameters.
The Texas Instruments - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor.
Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, an IEEE 754-compliant single-precision Floating-Point Unit (FPU), and Memory Protection Unit (MPU).
The single-precision processing capability on this unit provides us with the dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
The 64 kB of SRAM provides sufficient space to process our algorithms.
The 256 kB is more than enough flash memory to store the program and data references.
